
% Copyright (c) 2014 Connor Taffe <cpaynetaffe@gmail.com>
% licensed under the MIT license <opensource.org/licenses/MIT>

% Imports, etc.

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
}

\usepackage{fontspec}
% add tabular command

\newcommand{\btab}[2]{
	\bgroup
	\def\arraystretch{#1}
	\begin{tabular}{#2}
}

\newcommand{\etab}{
	\end{tabular} \smallskip
	\egroup
}

\name{Connor Taffe} % Your name
\address{(501) 606-1807 \\ \href{mailto:cpaynetaffe@gmail.com}{cpaynetaffe@gmail.com} \\
\href{http://byteflame.org}{byteflame.org}} % Your phone number and email

\begin{document}

% Work Experience
\begin{rSection}{Experience}

% Acxiom
\begin{rSubsection}{Apptegy}{January 2017}{Software Engineer}{Little Rock, Arkansas}

	\item Lead transition from monolithic Rails application to Ruby (\href{http://roda.jeremyevans.net/}{Roda}+\href{http://sequel.jeremyevans.net/}{Sequel}) \href{https://www.docker.com/}{containerized} microservices.
	\item Introduced \href{https://memcached.org/}{memcached} caching via \href{http://sequel.jeremyevans.net/rdoc-plugins/classes/Sequel/Plugins/Caching.html}{Sequel} ($\frac{1}{4}$ latency on average for cached requests).
	\item Introduced and implemented \href{https://www.openapis.org/}{OpenAPI} (Swagger 2.0) specifications during rearchitecture.
	\item Implemented CI (tests, style checking) and CD (docker build, push to registry) with \href{https://jenkins.io/}{Jenkins} for rearchitecture.
	\item Developed and containerized internal services: HKP GPG key server (initially deployed for \href{https://github.com/AGWA/git-crypt}{storing encrypted secrets in version control}), \href{https://www.openapis.org/}{OpenAPI} \href{https://github.com/Rebilly/ReDoc}{documenation server}, \href{https://jenkins.io/}{Jenkins} build server, \href{https://matrix.org/}{Matrix} chat server, \href{https://github.com/jeremyevans/kaeruera}{KaeruEra} error tracker.
\end{rSubsection}

% Acxiom
\begin{rSubsection}{Acxiom}{September - December 2016}{Entry Software Engineer}{Conway, Arkansas}

	\item Big data processing with Apache Hadoop and Spark
	\item Explored optimization techniques using Apache Spark
\end{rSubsection}


% All Electric Supply
\begin{rSubsection}{All Electic Supply}{June - September 2016}{Programmer}{Little Rock, Arkansas}

	\item Heavy usage of PostgreSQL SQL, {\tt psql}
	\item Use of Docker for testing based on production database backup
	\item Wrote helper programs in Go to send emails and perform regular queries
	\item Submitted accepted PRs to xTuple (ERP software)
\end{rSubsection}

% Ensono
\begin{rSubsection}{Ensono (formerly Acxiom ITO)}{October 2015 - May 2016}{Entry Applications Developer}{Conway, Arkansas}

	\item Wrote and maintained software in C\# for the .NET platform.
	\item Developed applications in Node.js, Golang, and Python for AWS Lambda.
	\item Versioned software in Git and maintained repositories in Bitbucket.
	\item Participated in Agile training and worked as part of a scrum team.
\end{rSubsection}

% EIT IT
\begin{rSubsection}{UALR EIT IT}{August - October 2015}{Student Worker}{Little Rock, Arkansas}

	\item Resolved technology related issues for staff and students.
	\item Tracked issues in ticketing system.
	\item Installed and Setup Microsoft Windows, including joining to Active Directory domain.
\end{rSubsection}

% SUPER Program
\begin{rSubsection}{EIT SUPER, UALR}{May - August 2015}{SUPER Scholar}{Little Rock, Arkansas}

	\item Summer Undergraduate Program of Entrepreneurship and Research (SUPER).
	\item Creation of an \href{http://github.com/cptaffe/flamethrower}{Android application}, written in Scala, to interface with a vehicle's OBD-II system via Bluetooth transmitter.
\end{rSubsection}

% Emerging Analytics Center
\begin{rSubsection}{Emerging Analytics Center (EAC), UALR}{October 2014 - May 2015}{Software Engineering Intern}{Little Rock, Arkansas}
	\item Presented at IEEE VR 2015 on the integration of Unity 3D, Qualcomm's Vuforia, and Intel's OpenCV to create interactive Augmented Reality (Arkansas) applications (\href{http://byteflame.org/ieee_vr/}{presentation}{}).
	\item Used Unity 3D (scripting with C\#) for 3D programming and model manipulation.
\end{rSubsection}

% Research Assistant
% \begin{rSubsection}{UALR Bioinformatics}{August - October 2014}{Research Assistant}{Little Rock, Arkansas}
%
% 	\item Preliminary work on refactoring a genetic algorithm codebase with an emphasis on common stylistic guidelines and concurrency.
% \end{rSubsection}

\end{rSection}

% sections wrapping pages looks junky
\clearpage


% Education Section

\begin{rSection}{Education}

\begin{rSubsection}{University of Arkansas, Little Rock}{}{Pursued a B.S. in Computer Science}

	\item Vice President of the UALR instance of the Association of Computing Machinery; Fall 2016
	\item Substantail completed courses: Calculus I, II; Discrete Math; Linear Algebra. Data Structures and Algorithms, Computer Systems and Assembly Language, Operating Systems, Databases, Computer Organization, Monte Carlo Simulation, Independent study on Compiler Design, Artificial Intelligence, Langauge Structures, Computer Security.
\end{rSubsection}

\begin{rSubsection}{Arkansas School for Mathematics, Sciences, and the Arts}{}{Attended}

	\item Substantial completed courses: Programming II, Physics I.
\end{rSubsection}

\end{rSection}

% Personal Projects
\begin{rSection}{Personal Projects}

\begin{rSubsection}{\href{http://github.com/cptaffe/birch}{birch}}{August 2016}{}{}

	\item IRC Bot in C
	\item Lexing/parsing of messages using state machine
\end{rSubsection}

% Lispy project
\begin{rSubsection}{\href{http://github.com/cptaffe/lispy}{Lispy}}{September - November 2014}{}{}

	\item Lisp-like interpreter written in Python
	\item Producer-consumer threading optimizes stages
	\item Lazy-evaluation of defined variables
	\item lambda functions and recursive lambdas
	\item EBNF formal definition of the language
\end{rSubsection}

% utf8 project
\begin{rSubsection}{\href{http://github.com/cptaffe/utf8}{utf8} / \href{http://github.com/cptaffe/utf8plus}{utf8plus}}{February 2015}{}{}

	\item utf8 parser written in C, and C++ wrapper.
	\item RFC 3629 compliant.
	\item Quick encoding/decoding of runes, rune validation, and string parsing.
	\item Reports errors within the rune and codepoint ({\tt int32\_t}) types using approprate non-valid values in C.
	\item Use of the \verb!utf8::rune::exception! class to report errors in C++, or appropriate C++ standard exception.
\end{rSubsection}

% bf project
\begin{rSubsection}{\href{http://github.com/cptaffe/bf}{bf}}{November 2014}{}{}

	\item Optimizing BrainFuck just-in-time compiler
	\item Emits {\tt x86\_64} instructions to executable {\tt mmap}'d pages
	\item Producer-Consumer concurrent architecture with a REPL interface
\end{rSubsection}

\end{rSection}

% Technical Strengths

\begin{rSection}{Technical Strengths}

{\bf General Programming}

\btab{1.1}{ l l }
	Languages: &  Ruby, Go, C, C++, Python, JavaScript, Typescript, (X)HTML, CSS, \\
	& Scala, Java, C\#, Rust, Php \\
	Libraries: & Roda, Sequel, Rails, Vue.js, Android SDK, Bootstrap \\
	Systems: & Hadoop, Spark \\
	Tools: & Docker, Git, Make, Ninja, CMake, Gradle \\
	Databases: & PostgresSQL \\
	OS: & Linux, Windows \\
\etab

\end{rSection}

\end{document}
